Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-09-26 manuscript/sections/results.tex
results: remove redundant plots from main text

The cost premium of 24/7 hourly clean electricity procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
Indeed, in the periods when not much wind or solar is available, matching every kilowatt-hour of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
Battery storage technology is cost-optimal for shifting surplus a power supply by a couple of hours. 
However, bridging extended periods of low wind and sun with battery storage is expensive.
Results above also illustrate that for CFE targets of 98\%--100\%, 24/7 participating consumers rely little on the grid supply, since electricity mix in the local grids contain some carbon content.

%TODO CCS has to be defined first above
The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies: 
long-duration energy storage (\gls{ldes}) and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.

%TODO maybe remove footnote when tech cost table is there
The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., the \gls{ldes} complements onshore wind, solar PV and battery storage.%
\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.}
The \gls{ldes} helps to align the load with the generation of procured variable renewable resources. 
As a result, the cost-optimal portfolio of renewable capacity for the 100\% 24/7 CFE target is not much larger than for the 100\% annual matching policy. 
This also significantly decreases procurement costs at high CFE targets: with \gls{ldes}, 100\% 24/7~CFE has a cost premium of 42\% above 100\% annual mathing with renewable energy.

The bottom row shows the results for the \textbf{palette~3} scenario (\cref{fig:10-2025-IE-p3-ci_capacity} and \cref{fig:10-2025-IE-p3-ci_costandrev}). 
In this scenario, 24/7~CFE participants have an access to the palette~2 technologies, as well as the clean firm generators, such as advanced geothermal and Allam cycle generators.
In the case of Ireland, the procurement strategy now includes the Allam cycle technology in the optimal mix.
The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on hourly basis.
Inclusion of clean firm generation reduces renewable capacity and storage requirements. 
This, in turn, further limits the 24/7 CFE cost premium.
In this scenario, 100\% 24/7~CFE costs only 15\% above 100\% annual renewable matching.

%TODO remove two capacity figs for space reduction? adjust text
\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Portfolio capacity with LDES.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_capacity.pdf}
        \label{fig:10-2025-IE-p2-ci_capacity}
    \end{subfigure}% 
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy with LDES.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p2-ci_costandrev}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Portfolio capacity with LDES and clean firm generators.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_capacity.pdf}
        \label{fig:10-2025-IE-p3-ci_capacity}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy with LDES and clean firm generators.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p3-ci_costandrev}
    \end{subfigure}
    \caption{Procurement of clean resources and energy storage if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies.
    The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) 
    if \gls{ldes} is available on the market.
    The bottom row shows the power capacity portfolio (\cref{fig:10-2025-IE-p3-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p3-ci_costandrev}) 
    for a case when both \gls{ldes} and clean firm dispatchable generators are available.}
    \label{fig:10-2025-IE-p23-ci_procurement}
\end{figure*}

@@

    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left panel)} and Poland \textbf{(right panel)} follows 24/7 hourly clean electricity procurement. Selected scenario with technological palette~3.}
    \label{fig:10-2025-DEPL-p3-4plots}
\end{figure*}

@@

The cost breakdown for Ireland 2030 shows that 24/7 hourly matching costs are decreasing for all technological pallets compared to 2025, see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}.
The reason is that 24/7 participating consumers benefit from lower prices for clean energy technologies and cleaner electricity grids. 
The results show that cost-optimal portfolios procured by \gls{ci} participants for the 100\% hourly matching with CFE policy have a very limited premium over the 100\% annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available. 
Through these low cost premiums, participating consumers achieve zero emissions associated with their electricity consumption and have a great impact on system-level \co emissions.

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}138
        \caption{Costs of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

>>>>

The cost premium of 24/7 hourly \gls{cfe} procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
Indeed, in the periods when not much wind or solar is available, matching every kWh of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
Battery storage technology is cost-optimal for shifting surplus a power supply by a couple of hours.
However, bridging extended periods of low wind and sun with battery storage is expensive.
Also, the results above show that 24/7 participating consumers rely little on grid supply to reach CFE targets of 98\%--100\%, since a local grid's electricity mix almost always includes some fossil-fueled generation.

The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies, including \gls{ldes} and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.

\cref{fig:10-2025-IE-p2-ci_costandrev} (left panel) shows the breakdown of costs for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., \gls{ldes} complements onshore wind, solar PV and battery storage.
A \gls{ldes} system\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.} helps to bridge hours with no renewable feed-in. 
As a result, the required portfolio of renewable capacity and procurement costs are reduced, especially for high CFE targets.
Thus, 100\% 24/7 hourly matching has a cost premium of 42\% above annual matching policy, which is significantly lower than w/o \gls{ldes}.

\cref{fig:10-2025-IE-p3-ci_costandrev} (right panel) illustrates \textbf{palette~3} scenario, i.e., 24/7 participants have an access to all palette~2 technologies, as well as to clean firm generation technologies.
Allam cycle generator with \gls{ccs} is now part of the optimal procurement strategy.
As CFE targets increase, the cost-optimal share of clean firm technology increases.
The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on an hourly basis.
The cost premium for 24/7 CFE is further reduced in this case: the 100\% 24/7 CFE costs only 15\% over 100\% annual renewable matching.

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy with LDES.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy with LDES and clean firm generators.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
        \label{fig:10-2025-IE-p3-ci_costandrev}
    \end{subfigure}
    \caption{The breakdown of costs per procurement policy if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies:
    w/ \gls{ldes} (\cref{fig:10-2025-IE-p2-ci_costandrev});
    w/ \gls{ldes} and clean firm generation technologies (\cref{fig:10-2025-IE-p3-ci_costandrev}).
    }
    \label{fig:10-2025-IE-p23-ci_procurement}
\end{figure*}

@@

    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left)} and Poland \textbf{(right)} follows 24/7 hourly clean electricity procurement. Selected scenario with technological palette~3.}
    \label{fig:10-2025-DEPL-p3-4plots}
\end{figure*}

@@

The cost breakdown for Ireland 2030 shows that 24/7 hourly matching costs are decreasing for all technological pallets compared to 2025, see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}.
The reason is that 24/7 participating consumers benefit from lower prices for clean energy technologies and cleaner electricity grids. 
The results show that cost-optimal portfolios procured by 24/7 participants for the 100\% hourly matching policy have a minor cost premium over the annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available. 
Through these low cost premiums, participating consumers achieve zero emissions associated with their consumption and have a great impact on system-level \co emissions.

@@

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \caption{Costs of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%
